A thesis draft

### 2018-12-02 res/sections/25-TestsResponsiveness.tex
Swap table columns, add saved configurations

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|c|c}
                     & \textbf{Standard deviation (seconds)} & \textbf{Average 
start up time (seconds)} \\ \hline
\textbf{Docker}      & 0.009620874                           & 0.016        \\
\textbf{Virtual Box} & 0.755                                 & 20.211
\end{tabular}%
}
\caption[Docker vs Virtual Box start up times comparison]{Docker vs Virtual Box
  start up times comparison. Is possible to see how the overall time required to
  start $100$ containers is less than the time to start one traditional virtual
  machine. The overall time required by the traditional virtualization system is
  approximately of 33 minutes, witch gives a significant insight of how much
  time is required to create and boot a virtualized environment.}
\label{my-label}
\end{table}

@@

% TODO is it worth to keep it as a long table?
\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Standard deviation (seconds)} & \textbf{Average 
deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13.291                     \\
\textbf{2}          & 0.6301444                  & 14.207                     \\
\textbf{3}          & 1.14903                    & 15.345                     \\
\textbf{4}          & 3.592179                   & 16.453                     \\
\textbf{5}          & 0.9728132                  & 16.634                     \\
\textbf{6}          & 1.103802                   & 17.418                     \\
\textbf{7}          & 2.944699                   & 17.984                     \\
\textbf{8}          & 1.733722                   & 18.480                     \\
\textbf{9}          & 1.746296                   & 18.607                     \\
\textbf{10}         & 1.291508                   & 20.511                     \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\

\end{longtable}

>>>>

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|c|c}
                     & \textbf{Average start up time (seconds)} & \textbf{Standard deviation (seconds)} \\ \hline
\textbf{Docker}      & 0.016                                    & 0.009620874                           \\
\textbf{Virtual Box} & 20.211                                   & 0.755                                
\end{tabular}%
}
\caption[Docker vs Virtual Box start up times comparison]{Docker vs Virtual Box
  start up times comparison. Is possible to see how the overall time required to
  start $100$ containers is less than the time to start one traditional virtual
  machine. The overall time required by the traditional virtualization system is
  approximately of 33 minutes, witch gives a significant insight of how much
  time is required to create and boot a virtualized environment.}
\label{chap:tests:sec:dockervsvb:tab:startup}
\end{table}

@@

\begin{longtable}[c]{c|c|c}
\textbf{SFC Length} & \textbf{Average deploy time (seconds)} & \textbf{Standard deviation (seconds)} \\ \hline
\endfirsthead
%
\endhead
%
\textbf{1} & 13.291 & 2.560102 \\
\textbf{2} & 14.207 & 0.6301444 \\
\textbf{3} & 15.345 & 1.14903 \\
\textbf{4} & 16.453 & 3.592179 \\
\textbf{5} & 16.634 & 0.9728132 \\
\textbf{6} & 17.418 & 1.103802 \\
\textbf{7} & 17.984 & 2.944699 \\
\textbf{8} & 18.480 & 1.733722 \\
\textbf{9} & 18.607 & 1.746296 \\
\textbf{10} & 20.511 & 1.291508 \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}
